Model of lens candidates from Space Warps CFHTLS

### 2016-07-13 paper2.tex
i commit that i thought I already commmited: the authors changes

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[R. K\"ung et al.]{
Rafael K\"ung,$^{1}$\thanks{E-mail: rafael.kueng@uzh.ch}
Prasenjit Saha,$^{1}$
Lucy Oswald$^{3}$
%and Fourth Author$^{4}$
\\
% List of institutions
$^{1}$Physik Institut, University of Zurich, Winterthurerstrasse XXX, Zurich 8057, Switzerland\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
%$^{4}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor

\author[Küng et al]{Rafael Küng,$^{1}$
Prasenjit Saha,$^{1}$
Ignacio Ferreras,$^{2}$
Anupreeta More,$^{3}$
Elisabeth Baeten,$^{4}$
\newauthor
Jonathan Coles,$^{5}$
Claude Cornen,$^{4}$
Christine Macmillan,$^{4}$
Phil Marshall,$^{6}$ 
Lucy Oswald$^{7}$
\newauthor
Aprajita Verma$^{8}$
and Julianne K. Wilcox$^{4}$
%
\\
%
$^{1}$Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland\\
$^{2}$\\
$^{3}$Kavli Institute for the Physics and Mathematics of the Universe, University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa-shi 277-8583, Japan\\
$^{4}$Zooniverse, c/o Astrophysics Department, University of Oxford, Oxford OX1 3RH, UK \\
$^{5}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France\\
$^{6}$Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA\\
$^{7}$\\
$^{8}$Sub-department of Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
}
